06_DESeqALL

### 2019-12-03 analysis/06_DESeq2_ALL.Rmd
now with musical prolactin

## DEseq2 analysis on characterization. Looking at treatment AND sex for each tissue

@@

@@

```{r pitplot, eval = T}
a <- plot.volcano(inc.d3.m.inc.d3 , "treatment",   "m.inc.d3", "inc.d3",   colorsvolcano)
b <- plot.volcano(inc.d9.m.inc.d9, "treatment",  "m.inc.d9", "inc.d9" , colorsvolcano)
c <- plot.volcano(inc.d17.m.inc.d17 , "treatment",  "m.inc.d17", "inc.d17" , colorsvolcano) 
d <- plot.volcano(hatch.m.n2 , "treatment",   "m.n2", "hatch", colorsvolcano) 
e <- plot.volcano(inc.d9.m.inc.d8 , "treatment",   "m.inc.d8", "inc.d9"  , colorsvolcano)
f <- plot.volcano(hatch.m.inc.d8 , "treatment",    "m.inc.d8", "hatch"  , colorsvolcano) 
g <- plot.volcano(inc.d17.prolong , "treatment",   "prolong", "inc.d17",  colorsvolcano) 
h <- plot.volcano(hatch.prolong , "treatment",  "prolong", "hatch", colorsvolcano) 
i <- plot.volcano(hatch.extend , "treatment",  "extend", "hatch" , colorsvolcano) 
j <- plot.volcano(n5.extend , "treatment",  "extend", "n5", colorsvolcano)

pituitary <- plot_grid(a +  theme(axis.title.x = element_blank(), axis.text.x = element_blank()) +
                       labs(y = "pituitary \n -log10(p)"),
          b + theme(axis.title = element_blank(), axis.text = element_blank()),
          c + theme(axis.title = element_blank(), axis.text = element_blank()),
          d + theme(axis.title = element_blank(), axis.text = element_blank()), 
          e + theme(axis.title = element_blank(), axis.text = element_blank()),
          f + theme(axis.title = element_blank(), axis.text = element_blank()),
          g + theme(axis.title = element_blank(), axis.text = element_blank()),
          h + theme(axis.title = element_blank(), axis.text = element_blank()), 
          i + theme(axis.title = element_blank(), axis.text = element_blank()), 
          j + theme(axis.title = element_blank(), axis.text = element_blank()), 
          nrow = 2)
pituitary
```

>>>>

# Warning: This script takes a very long time to run.

DESeq2 was not designed to run on 300 samples. But, I really like it, so I do it anyways. Some of these commands take like 15 min to run using 6 cores.

## DEseq2 on all chaacterization and manipulations

@@

```{r pitvsd, eval=T}
vsd <- as.data.frame(assay(vst(dds.pituitary, blind=FALSE)))
write.csv(vsd, "../results/06_pitallvsd.csv")
```

@@

```{r volcanos}
a <- plot.volcano(inc.d3.m.inc.d3 , "treatment",   "m.inc.d3", "inc.d3",   colorsvolcano) + 
  annotation_custom(lay, ymin = 20, ymax = 30, xmin = -8, xmax = -2) + 
  annotation_custom(bldg, ymin = 20, ymax = 30, xmin = 2, xmax = 8) 
b <- plot.volcano(inc.d9.m.inc.d9, "treatment",  "m.inc.d9", "inc.d9" , colorsvolcano)+ 
  annotation_custom(inc, ymin = 20, ymax = 30, xmin = -8, xmax = -2) + 
  annotation_custom(bldg, ymin = 20, ymax = 30, xmin = 2, xmax = 8) 
c <- plot.volcano(inc.d17.m.inc.d17 , "treatment",  "m.inc.d17", "inc.d17" , colorsvolcano) + 
  annotation_custom(inc, ymin = 20, ymax = 30, xmin = -8, xmax = -2) + 
  annotation_custom(bldg, ymin = 20, ymax = 30, xmin = 2, xmax = 8) 
d <- plot.volcano(hatch.m.n2 , "treatment",   "m.n2", "hatch", colorsvolcano) + 
  annotation_custom(hatch, ymin = 20, ymax = 30, xmin = -8, xmax = -2) + 
  annotation_custom(bldg, ymin = 20, ymax = 30, xmin = 2, xmax = 8)

e <- plot.volcano(inc.d9.m.inc.d8 , "treatment",   "m.inc.d8", "inc.d9"  , colorsvolcano)  +
  annotation_custom(inc, ymin = 20, ymax = 30, xmin = -8, xmax = -2) + 
  annotation_custom(hatch, ymin = 20, ymax = 30, xmin = 2, xmax = 8) 
f <- plot.volcano(inc.d17.prolong , "treatment",   "prolong", "inc.d17",  colorsvolcano)  +
  annotation_custom(inc, ymin = 20, ymax = 30, xmin = -8, xmax = -2) + 
  annotation_custom(inc, ymin = 20, ymax = 30, xmin = 2, xmax = 8) 
g <- plot.volcano(hatch.prolong , "treatment",  "prolong", "hatch", colorsvolcano)  +
  annotation_custom(hatch, ymin = 20, ymax = 30, xmin = -8, xmax = -2) + 
  annotation_custom(inc, ymin = 20, ymax = 30, xmin = 2, xmax = 8)

h <- plot.volcano(hatch.m.inc.d8 , "treatment",    "m.inc.d8", "hatch"  , colorsvolcano)  +
  annotation_custom(hatch, ymin = 20, ymax = 30, xmin = -8, xmax = -2) + 
  annotation_custom(hatch, ymin = 20, ymax = 30, xmin = 2, xmax = 8) 
i <- plot.volcano(hatch.extend , "treatment",  "extend", "hatch" , colorsvolcano)  +
  annotation_custom(hatch, ymin = 20, ymax = 30, xmin = -8, xmax = 2) + 
  annotation_custom(hatch, ymin = 20, ymax = 30, xmin = 2, xmax = 8) 
j <- plot.volcano(n5.extend , "treatment",  "extend", "n5", colorsvolcano)  +
  annotation_custom(hatch, ymin = 20, ymax = 30, xmin = -8, xmax = -2) + 
  annotation_custom(nestling, ymin = 20, ymax = 30, xmin = 2, xmax = 8)

remove <- plot_grid(a +  theme(axis.title.x = element_blank(), axis.text.x = element_blank()) +
                       labs(y = "pituitary \n -log10(p)", subtitle = "1771 DEGs"),
          b + theme(axis.title = element_blank(), axis.text = element_blank()) + labs(subtitle = "277 DEGs"),
          c + theme(axis.title = element_blank(), axis.text = element_blank()) + labs(subtitle = "3909 DEGs"),
          d + theme(axis.title = element_blank(), axis.text = element_blank()) + labs(subtitle = "3162 DEGs"), 
          nrow = 1, rel_widths = c(1.2,1,1,1),
          labels = c("a","b","c","d"), label_size = 9)
remove

manipinc <- plot_grid(e +  theme(axis.title.x = element_blank(), axis.text.x = element_blank()) +
                       labs(y = "pituitary \n -log10(p)", subtitle = "120 DEGs"),
          f + theme(axis.title = element_blank(), axis.text = element_blank()) + labs(subtitle = "1007 DEGs"),
          g + theme(axis.title = element_blank(), axis.text = element_blank()) + labs(subtitle = "731 DEGs"),
          nrow = 1, rel_widths = c(1.2,1,1),
          labels = c("e","f","g"," "), label_size = 9)

maniphatch <- plot_grid( h +  labs(subtitle = "4113 DEGs"), 
          i + theme(axis.title.y = element_blank(), axis.text.y = element_blank()) + labs(subtitle = "1894 DEGs"), 
          j + theme(axis.title.y = element_blank(), axis.text.y = element_blank()) + labs(subtitle = "256 DEGs"), 
          nrow = 1, rel_widths = c(1.2,1,1),
          labels = c("h","i","j"," "), label_size = 9)

plot_grid(manipinc, maniphatch, nrow = 2)
```
